---
title: "hw2.Rmd"
author: "Yuanyou Yao yyao93@wisc.edu"
date: "2020/10/2"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
```

At the beginning, I tried to find the most important character of cB58, which is the trough. So in the first part of my code, I wanted to locate the most possible alignment of other spectra. I used correlation as criterion. After cleaned the data points with and_mask != 0, I had intervals with length 350, which determined by cB58's trough. I primarily chose top 20 spectra and spec-1353-53083-0579.fits. was at No.18.


Then I simply wanted to some other significant characters like some small values in spectra. Instead of considering the whole "shape" of the spectra, the distance between small values and the trough would show whether the two spectra looks like or not in some degree. I calculated the difference of indices and I got 101 vectors(including cB58's) with 10 elements. I then used correlation again and got the result.

However, the result was not ideal, spec-1353-53083-0579.fits was not in top 3, not even in top 10. I think the problems with this method is that the 10 smallest values may fall into trough's interval. In other words, what I calculated in step2 is a local shape rather than global. The consequece is that it won't change the rank much in step 1, since it was already a local character.
```{r message=FALSE, warning=FALSE}
rm(list=ls())
library("FITSio")
path="./data"
fileNames=dir(path)
filePath=sapply(fileNames,function(x){paste(path,x,sep='/')})
data=lapply(filePath,function(x){readFrameFromFITS(x)})
cB58=readFrameFromFITS("cB58_Lyman_break.fit")
cB58_trough = cB58[1:351,]
cB58_local_min = which.min(cB58_trough[,2])
cB58_global = rank(cB58[,2])[1:10]
cB58_distance = cB58_global - cB58_local_min
data_new = NULL
for (i in 1:length(data)) {
data_new[[i]]=data[[i]][data[[i]][,4]==0,c(1,2)]
}
    data_new[[97]] = NULL
min_global =NULL
distance = NULL
for (i in 1:length(data_new)){
  for (j in 351: nrow(data_new[[i]])){
   distance[j-350]= cor(data_new[[i]][(j-350):j,1],cB58_trough[,2] )
  }
  min_global[[i]] = c(max(distance),which.max(distance)+350)
}
a=t(as.data.frame(min_global))
b=sort(a[,1],index.return =T)$ix[80:99]
data_new_distance = NULL
for(i in 1:length(b)){
  c =which.min(data_new[[b[i]]][a[b[i],2]:(a[b[i],2]+351),1])
  d = sort(data_new[[b[i]]][,1],index.return=T)$ix[1:10]
  data_new_distance[[i]] = d-c
}
data_new_distance[[8]] = NULL
e = NULL
for (i in 1:(length(b) - 1)) {
  e[i] = cor(data_new_distance[[i]],cB58_distance)
  
}
sort(e,decreasing = T,index.return = T)$ix

```

I finally use the Euclidean Distance to measure, here is the result.
```{r}
x = read.csv('hw2.csv')
y = x$V2
fileNames=y[1:3]
filePath=sapply(fileNames,function(x){paste(path,x,sep='/')})
data=lapply(filePath,function(x){readFrameFromFITS(x)})
for(i in 1:3){
plot(y = data[[i]][,1],x = 1:nrow(data[[i]]))
  points(y = cB58[,2], x=x$V3[i]:(x$V3[i]+2180), col = 'red')
  legend("topleft",pch = c(1,1),legend =c(fileNames[i],"cB58"),col=c("black","red"))
}

```

